Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-13 cosmic_voids.tex
Section 5.2, The void size distribution, done

We use the Bolshoi simulation to test the method describe in the
paper. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
This values are consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We find the cosmic web we estimate first the density and velocity
fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a spatial resolution of $0.98$\hMpc per cell
side.  
These fields are smoothed with a gaussian filter with a width of
$\sigma=0.98$\hMpc.
We compute the tidal and shear tensors through finite-differences and
Finally, the eigenvalues and eigenvectors of the tensor are
obtained for each grid cell.
The data we use here is publicly available through the MultiDark
database \url{http://www.multidark.org/MultiDark/} which is described
in \citet{Riebe11}.

@@

%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@

\end{figure*}
\end{flushleft}
%.........................................................................

@@

%-------------------------------------------------------------------------
\subsection{Enclosed mass}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------thereby allowing a good classification criterion

When we analyse individual density profiles of voids (see left panels of
Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
families, differentiated by the presence or absence or a compensation 
ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to discriminate 
each void in one of the families, we propose the compensation index, which 
is defined as the mass of a void enclosed at a spherical volume of radius $R$ 
and normalized by the mass of the same volume as assuming the mean background
density instead

@@

We choose an integration radius of $R=4r_{eff}$, which is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ have more mass than expected, 
constituting the family of overcompensated voids. These voids generally 
exhibit a compensation ridge. In the same fashion, voids with 
$\mathcal{C}<1$ constitute the family of subcompensated voids.

@@

%.........................................................................
%FIGURE 3: volume functions
\begin{flushleft}
\begin{figure}
\centering

@@

  \label{fig:volume_function}
  \vspace{0.1 cm}

\end{figure}
\end{flushleft}
%.........................................................................

@@

%.........................................................................

%\end{figure*}
%\end{flushleft}
%.........................................................................

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}

@@

\end{figure*}
\end{flushleft}
%.........................................................................

\end{document}

>>>>

We use the Bolshoi simulation to test the method describe in the
paper. 
This simulation follows the non-linear evolution of a dark
matter density field on a cubic volume of  size $250$\hMpc\ sampled
with $2048^3$ particles. 
The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
constant, dimensionless Hubble parameter, spectral index of
primordial density perturbations and normalization for the power
spectrum, respectively. 
This values are consistent with the seventh year of data of the Wilkinson 
Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
For more detailed  technical information about the simulation, see
\citet{Klypin11}.

We find the cosmic web we estimate first the density and velocity
fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
side.  
These fields are smoothed with a gaussian filter with a width of
$\sigma=0.98$\hMpc.
We compute the tidal and shear tensors through finite-differences and
Finally, the eigenvalues and eigenvectors of the tensor are
obtained for each grid cell.
The data we use here is publicly available through the MultiDark
database \url{http://www.multidark.org/MultiDark/} which is described
in \citet{Riebe11}.

@@

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering

@@

\end{figure*}
%.........................................................................

@@

%-------------------------------------------------------------------------
\subsection{Enclosed mass}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

When we analyse individual density profiles of voids (see left panels of
Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
families, differentiated by the presence or absence of a compensation 
ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to 
discriminate each void in one of the families, we propose the compensation 
index $\mathcal{C}$, which is defined as the mass of a void enclosed in a 
spherical volume of radius $R$ and normalized by the mass of the same 
volume as assuming the mean background density instead

@@

We choose an integration radius of $R=4r_{eff}$, that is large enough to 
enclose the compensation ridge for a typical void in case there is one. 
This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
constituting the family of overcompensated voids. These voids generally 
exhibit a compensation ridge associated to dense nearby structures. In the 
same fashion, voids with $\mathcal{C}<1$ constitute the family of 
subcompensated voids.

@@

%.........................................................................
%FIGURE 3: volume functions
\begin{figure}
\centering

@@

  \label{fig:volume_function}

\end{figure}
%.........................................................................

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $r_{eff} = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.

In Fig. \ref{fig:volume_function} we show the void size distributions
for both schemes and for the overall distribution of voids as well as for 
overcompensated and subcompensated void subsamples. The central region of
the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
shape, contrary to expected from highly non-linear structures like dark 
matter halos, where the abundances increase for smaller structures. 
The distribution of the FA-Tweb is consistent with a two-barrier problem 
\citep{Sheth04}: formation of large voids is inhibited by the 
\textit{void-in-void} problem (first barrier), where large voids are 
constituted hierarchically of smaller ones. In turn, formation of small 
voids is damped by the \textit{void-in-cloud} problem (second barrier), 
where nearby collapsing structures limit the abundance of embedded small 
voids.

The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
problem as it predicts large abundances of smaller voids. However, an 
interesting result is the difference between the overcompensated and 
subcompensated subsamples. Subcompensated voids, which are expected to 
be embedded in low-density regions like walls and larger voids, exhibit
smaller abundances compatible with the result of the FA-Tweb. Then, the 
most dramatic contribution to the overabundance of small voids for the 
FA-Vweb comes from overcompensated voids. This implies that, although
nearby non-linear structures squeeze out embedded smaller voids, the
rapid and isotropic collapse in these zones, along with the more rugged 
nature of the velocity field make these voids still detectable by this 
scheme.

For both schemes overcompensated voids are more abundant, however at 
larger scales abundances of subcompensated voids become comparable. This 
is somehow expected as larger voids are more likely to abut other voids.
A recent estimation of the radius of the local void gives $r_{LV}\approx
10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
$h = 0.70$, the size of the local void would be around $r_{eff} = 7$
\hMpc\ in the shown distribution. For both schemes, this places the local
void as a rather common void in terms of size, and more likely to be
overcompensated.

@@

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}

@@

\end{figure*}
%.........................................................................

%\end{figure*}
%\end{flushleft}
%.........................................................................
\end{document}
